Are We Reusing Outdated and License-Violating \newline Code Snippets from Stack Overflow?

### 2017-02-05 cloneoverflow-latex/cloneoverflow.tex
Updated the outdated pair table.

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 525 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,444 & 3,502 & 670 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

%We selected only Stack Overflow fragment and Qualitas files that have never been looked at before in the previous investigation. If many clone pairs having the same Stack Overflow fragment and Qualitas file, we keep only the largest one. The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stack Overflow fragments or Qualitas files. The classification results are shown in Table \ref{tab:classification_indv}.

%\begin{table}
%	\centering
%	\caption{No.~of disagreed clone pairs ($S_D$ and $N_D$).}
%	\label{tab:classification_indv_stats}
%	\small
%	\resizebox{\columnwidth}{!}{%
%	\begin{tabular}{l|p{1.6cm}|r|r|r|r}
%		\hline 
%		Tool & Filter & \multicolumn{1}{c|}{Original} & \multicolumn{1}{c|}{Filtered} & \multicolumn{1}{c|}{good/ok} & \multicolumn{1}{c}{remaining} \\ 
%		%\hline 
%		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
%		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
%		\hline
%		\multirow{1}{*}{\textit{Simian$_{df}$}} & $Line \geq 10$ \newline \& RegEx & \multirow{2}{*}{67,570} & \multirow{2}{*}{47,223}  & \multirow{2}{*}{2,546} & \multirow{2}{*}{17,801} \\ %140 + 1482 + 926
%		\hline
%%		\multirow{1}{*}{\textit{$N_D$}-1} & 7040  & 226 & 6700 & 114 \\
%%		\multirow{1}{*}{\textit{$N_D$}-2} & 22187  & 152 & 21990 & 45 \\
%		\multirow{1}{*}{\textit{$N_D$}} & $Sim \geq 80\%$ \newline \& RegEx & \multirow{2}{*}{229,176} & \multirow{2}{*}{228,558}  & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
%		\hline
%		%\multicolumn{2}{l|}{Total} & 296,746 & 20,966 & 2,996 & 1,039 \\
%		%\hline
%	\end{tabular} %
%	}
%\end{table}

@@

There were 32,039 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}. We have use regular expressions to automatically classify \texttt{equals()} methods based on the method signature since they are not very interesting clones. It captured 28,444 clone pairs and classified them into pattern D. With help of the automatic classification, there were 3,595 pairs left for manual classification.

The first author who has been working on clone detection research for two years took the role of a main investigator performing a manual classification of all the 3,595 clone pairs. By consulting the cloning patterns, the main investigator manually went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair. A relevant and useful observation was also recorded for each clone pair. The second author took the role of a validating investigator performing 10\% validation (359 pairs) of the clone pairs judged by the main investigator. The two investigators discussed 54 classification conflicts and resolved 51 of them. The 3 conflicts which the two investigators could not find consensuses are resolved after involving the third author.

The classification results are shown in \Cref{tab:classification_good_o}. For \textit{good} pairs, 9 pairs were automatically classified by regular expressions and 2,299 pairs were manually classified. This resulted in one clone pair in pattern QS which is found to be copied from a Qualitas project to Stack Overflow. Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern UD. We observed 3 pairs in pattern ES since they are copied from external sources. 58 clone pairs are found to be pattern BP. Six pairs are similar code from inheriting the same superclass or implementing the same interface, pattern IN. Finally, 2,189 pairs are false clones and classified into FC. No clones were found in pattern SQ. This was expected since we selected a pretty old Qualitas snapshot dated back 2013 and most of the code could be written long before that.

For the \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually.  Consulting the classification of \textit{good} pairs, we found that $S_EN_E$ produces a large number of x,xxx false positive results (accounts for xx.xx\% of $S_EN_E$ clone pairs) due to its recall preference. We thus decided to ignore this clone set in our \textit{ok}-pair classification. A large number of 11,495 clone pairs were automatically classified and 254 pairs were done manually. We found xx, xx, xx, xx, xx, and xx in QS, UD, ES, BP, IN and FC respectively. Similarly, no clone pairs were found in SQ.

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP  & EX & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
			\hline
			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

For disagreed clone pairs, an automatic and manual classification of 17,801 $S_D$ and 181 $N_D$ clone pairs results in xx pairs in pattern QS, xx pairs in UD, xx pairs in ES, xx in BP, xx in IN and xx in FC.

\textbf{To answer RQ2, we found that ...}

@@

%\subsubsection{Outdated Clones}
Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the original code \cite{Bellon2007}. However, in this situation, the clones are pervasive on Stack Overflow posts and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the code snippets are still working as expected. Hence, if any change happens in the original code, our results show that the copies on Stack Overflow are still mostly left outdated.

As far as we know, our work is possibly the first which discovers outdated code on Stack Overflow. Since code can be updated due to various possible reasons, e.g.~bug fixing or API changes, it is risky if developers reuse outdated code snippets from Stack Overflow.
They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.

To check if the discovered Stack Overflow clones are outdated, we focused on the 96 QS clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}). For each code snippet, we tracked its original code in Qualitas projects. We located the latest version of the each file and compared to the Stack Overflow snippet to see if any change has been made to the source code. If we found any change, we used \textit{git blame} command to see who modified the source code and when.

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. The comparison with the clones' latest versions revealed that 55 clone pairs were outdated and they were all Stack Overflow accepted answers. \texttt{hadoop} and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from \texttt{eclipse-SDK}. An example of outdated code in \texttt{hadoop}'s \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). Lastly, we found some ``orphan'' snippets. These snippets cannot find their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

The outdated online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagations. An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers. Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.

\textbf{For RQ3, we found 55 code snippets on Stack Overflow that are outdated and questionable for being reused.}
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

@@

	\caption{58 code clones in Stack Overflow (SO) that were altered, rewritten, or removed from the project after posted and their respective licenses. Files can be changed ($C$) by modifications ($M$), deletion ($D$), and rewriting ($R$).}

@@

	\scriptsize

@@

	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|l|l|c|l}

@@

		No. & Project & Ver. & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\

@@

			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\

>>>>

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 & 525 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 & 670 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

@@

There were 31,946 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}. We have use regular expressions to automatically classify \texttt{equals()}, getter and setter methods  based on the method signature since they are not very interesting clones. As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP. With help of the automatic classification, there were 3,632 pairs left for manual classification.

The first author who has been working on clone detection research for two years took the role of a main investigator performing a manual classification of all the 3,632 clone pairs. By consulting the cloning patterns, the main investigator manually went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair. A relevant and useful observation was also recorded for each clone pair. The second author took the role of a validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator. The two investigators discussed 54 classification conflicts and resolved 51 of them. The 3 conflicts which the two investigators could not find consensuses were resolved by the third author.

The classification results are shown in \Cref{tab:classification_good_o}. For \textit{good} pairs, 10 pairs were automatically classified by regular expressions and 2,298 pairs were manually classified. This resulted in 3 clone pairs in pattern QS which is found to be copied from a Qualitas project to Stack Overflow. Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern UD. Please note that we were conservative in this study when doing classification. Even the clone pairs were exactly or almost identical but we could not find an evidence that it was cloned in any particular direction, we classified them as UD instead of QS, SQ, or EX. We observed 4 pairs in pattern EX since they are copied from external sources. 111 clone pairs are found to be pattern BP. Seven pairs are similar code from inheriting the same superclass or implementing the same interface, pattern IN. Finally, 2,172 pairs are false clones and classified into FC. No clones were found in pattern SQ. This was expected since we selected a pretty old Qualitas snapshot dated back 2013 and most of the code could be written long before that.

For \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually and decided to remove $S_EN_E$ from this round of classification. According to the classification of \textit{good} pairs, we found that $S_EN_E$ accounted for 98.9\% of all false positive pairs in \textit{good} pairs. This was not a surprise since EvaClone configurations prefered recall and hence offered relaxed configurations. We ignored them since we were more interested in meaningful clones. This resulted in 11,749 \textit{ok} pairs remaining. 11,494 clone pairs were automatically classified and 255 pairs were looked at manually. 
We found 12, 42, 23, 11,459, 20, and 103 in QS, UD, EX, BP, IN and AC respectively. Similarly, no clone pairs were found in SQ.

\begin{table}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 42 & 23 & 11,549 & 20 & 103 & 11,749 \\
			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 110 & 0 & 382 & 178 & 28,642 & 109 & 2,525 & 31,946 \\ 
			\hline
		\end{tabular} 
	}
\end{table}

For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code. Our regular expressions could automatically classified 16,800 of them into BP. The investigator checked the 1,001 remaining pairs manually. As a result, we found 86 QS, 294 UD, 145 EX, 17,074 BP, 74 IN and 128 AC pairs. For 88 $N_D$ clone pairs, 10 of them were automatically classified into BP and 78 were manually classified. We found 9 QS, 35 UD, 6 EX, 17 BP, 8 IN, and 13 AC respectively.

\textbf{To answer RQ2, we used our patterns of online code cloning to classified 31,946 clone pairs. Our results showed that although most of the clone pairs were boiler-plate code (28,642), clones from inheritance/interface (109), or accidental clones (2,525); there were 670 pairs that were very interesting. 110 pairs had strong evidences to be cloned from Qualitas to Stack Overflow. 382 were non-trivial clones but without strong evidence of clone direction. 178 pairs were found to be cloned from external sources outside Qualitas projects. Lastly, we did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

%\subsubsection{Outdated Clones}
To the best of our knowledge, this work is the first to discuss a problem of outdated code on Stack Overflow. Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the original code \cite{Bellon2007}. However, for online code clones, the clones are pervasive and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the code snippets are still working as expected.

To check if our online code clones are outdated, we focused on the 110 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions. We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016. For each online clone pair, we used the file name of Qualitas clone to search for its latest version. Once we found the file, we located the location of the cloned snippets in the file based on method names. So for Simian clones that may not contain in a single method, we looked further up and down the clone region to get the method name and its nearby methods. We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code. We also made sure that the changes did not come from modifications maded to Stack Overflow snippets by the posters but from the projects themselves. When we found inconsistent lines between the two versions, we used \texttt{git blame} command to see who modified those lines of code and noted down the details.

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. We discovered 59 outdated online clone pairs out of 110 pairs. \texttt{spring} and \texttt{hibernate} have the maximum number of 20 outdated pairs, followed by 15 from \texttt{eclipse}, and 12 from \texttt{hadoop}. An example of outdated code in \texttt{hadoop}'s \texttt{WritableComparator.java} has already been shown in \Cref{fig:before-after}. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of \texttt{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). We also found 3 ``dead'' snippets. These snippets did not have their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of \texttt{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

The outdated online code clones can cause problems ranging from uncompilable code (due to modifications and different API usage in the outdated code) to bug propagations. An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers. Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive enough for naive developers who are ignorant to copy and reuse the code.

\textbf{For RQ3, our results show that more than half (59) of QS clone pairs on Stack Overflow are outdated. We observed that the newer versions of these outdated snippets contained various changes ranging from a slight modifications of variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures. Moreover, we found three dead snippets. They do not exist any more in the latest version. Both outdated and dead online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.  }
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from \texttt{SchemaUpdate.java} and its latest version in hibernate code base contains heavy modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

%\begin{table*}
%	\centering
%	\caption{62 QS outdated online code clones. Clones can be outdated by modifications ($M$), deletion ($D$), and rewriting ($R$).}
%	\label{tab:stale_code_details}
%	\scriptsize
%	\resizebox{2.1\columnwidth}{!}{%
%	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|c|l}
%		\hline 
%		No. & Project & Ver. & File & Start & End & SO Post & Cause & C$_{\textit{\textrm{date}}}$ \\
%		\hline
%			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & 18303692 & $M$  & 2015-09-08 \\
%			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & 18303692 & $M$  & 2015-09-08 \\
%			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & 2513183 & $M$  &  2015-03-17 \\
%			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 &  2513183	& $M$  &  2015-03-17 \\
%			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 &  2513183	& $M$  &  2015-03-17 \\
%			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 &  2513183	& $M$  & 2011-03-01 \\
%			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 &   11861598	& $M$  &  2011-02-03 \\
%			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & 21702608 & $M$  & 2011-06-12 \\
%			9 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 289 & 309 & 21702608 & $M$  & 2011-06-12 \\
%			10 & \texttt{hadoop} & 1.0.0 & JobSubmissionFiles.java  & 46 & 55 & 14845581 & $M$  & 2012-06-25 \\
%			11 & \texttt{hadoop} & 1.0.0 & mapred/../LineRecordReader.java  & 47 & 60 & 16180910 & $M$  & 2011-07-25 \\
%			12 & \texttt{hadoop} & 1.0.0 & mapreduce/../LineRecordReader.java  & 75 & 99 & 16180910 & $M$  & 2011-07-25 \\
%			13 & \texttt{hadoop} & 1.0.0 & StringUtils.java  & 40 & 56 & 801987 & $M$  & 2013-02-04 \\
%			14 & \texttt{hadoop} & 1.0.0 & TestJobCounters.java  & 186 & 192 & 18833798 & $M$  & 2011-06-12 \\
%			15 & \texttt{hadoop} & 1.0.0 & TextOutputFormat.java  & 75 & 99 & 16928749 & $M$  & 2011-06-12 \\
%			16 & \texttt{hadoop} & 1.0.0 & WritableComparator.java  & 44 & 54 & 22315734 & $M$  & 2014-11-20 \\
%			17 & \texttt{hibernate} & 4.2.2 & ConnectionProviderInitiator.java  & 65 & 93 & 15168494 & $M$  & 2012-06-24 \\
%			18 & \texttt{hibernate} & 4.2.2 & Example.java  & 224 & 243 & 24924255 & $M$  & 2013-04-23 \\
%			19 & \texttt{hibernate} & 4.2.2 & SchemaUpdate.java  & 115 & 168 & 23520731 & $M$  & 2016-02-05 \\
%			20 & \texttt{hibernate} & 4.2.2 & SettingsFactory.java  & 244 & 255 & 8257554 & $D$  & 2011-03-11 \\
%			21 & \texttt{hibernate} & 4.2.2 & SQLServer2005LimitHandler.java  & 43 & 61 & 23967852 & $M$  & 2015-03-12 \\
%			22 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 982 & 998 & 8037824 & $M$  & 2008-04-17 \\
%			23 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 1221 & 1240 & 8037824 & $M$  & 2011-05-20 \\
%			24 & \texttt{jfreechart} & 1.0.13 & AbstractXYItemRenderer.java  & 532 & 569 & 12936580 & $M$  & 2016-02-19 \\
%			25 & \texttt{jfreechart} & 1.0.13 & KeyToGroupMap.java  & 18 & 30 & 16058183 & $M$  & 2013-07-03 \\
%			26 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 502 & 520 & 21998949 & $M$  & 2008-06-02 \\
%			27 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 522 & 536 & 21998949 & $M$  & 2008-06-02 \\
%			28 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 16 & 22 & 6722760 & $R$  & 2014-04-13 \\
%			29 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 28 & 40 & 6722760 & $R$  & 2014-04-13 \\
%			30 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 31 & 36 & 6722760 & $R$  & 2014-04-13 \\
%			31 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 39 & 56 & 6722760 & $R$  & 2014-04-13 \\
%			32 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & 14940863 & $M$  & 2015-12-13 \\
%			33 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & 24680923 & $M$  & 2015-12-13 \\
%			34 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & 6025026 & $M$  & 2010-04-13 \\
%			35 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & 6025026 & $M$  & 2010-04-13 \\
%			36 & \texttt{junit} & 4.11 & Assert.java  & 33 & 52 & 23586872 & $M$  & 2015-05-12 \\
%			37 & \texttt{junit} & 4.11 & ExternalResource.java  & 4 & 23 & 7504040 & $M$  & 2016-06-25 \\
%			38 & \texttt{junit} & 4.11 & ExpectException.java  & 11 & 29 & 8802082 & $M$  & 2014-05-26 \\
%			39 & poi & 3.6 & WorkbookFactory.java  & 18 & 28 & 12593810 & $M$  & 2015-04-29 \\
%			40 & \texttt{spring} & 3.0.5 & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & 5660519 & $D$  & 2012-01-20 \\
%			41 & \texttt{spring} & 3.0.5  & AutowireUtils.java  & 32 & 42 & 20913543 & $M$  & 2014-10-28 \\
%			42 & \texttt{spring} & 3.0.5  & CustomCollectionEditor.java  & 33 & 71 & 18623736 & $M$  & 2013-11-21 \\
%			43 & \texttt{spring} & 3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & 3758110 & $D$  & 2012-01-20 \\
%			44 & \texttt{spring} & 3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & 6149818 & $M$  & 2013-03-19 \\
%			45 & \texttt{spring} & 3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2016-07-15 \\
%			46 & \texttt{spring} & 3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2008-12-18 \\
%			47 & \texttt{spring} & 3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2008-12-18 \\
%			48 & \texttt{spring} & 3.0.5  & DispatcherServlet.java  & 91 & 103 & 4781746 & $M$  & 2011-08-08 \\
%			49 & \texttt{spring} & 3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & 10924700 & $M$  & 2012-08-28 \\
%			50 & \texttt{spring} & 3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & 3751463 & $M$  & 2016-07-05 \\
%			51 & \texttt{struts2} & 2.2.1  & DefaultActionMapper.java  & 91 & 103 & 14019840 & $M$  & 2013-10-18 \\
%			52 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 25 & 73 & 21734562 & $M$  & 2016-08-04 \\
%			53 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 33 & 43 & 21734562 & $M$  & 2016-08-04 \\
%			54 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 543 & 553 & 24404964 & $M$  & 2012-11-18 \\
%			55 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 557 & 573 & 24404964 & $M$  & 2012-11-18 \\
%			56 & \texttt{tomcat} & 7.0.2  & FormAuthenticator.java  & 51 & 61 & 21734562 & $M$  & 2016-08-04 \\
%			57 & \texttt{tomcat} & 7.0.2  & HttpServlet.java  & 111 & 124 & 5266856 & $M$  & 2011-10-22 \\
%			58 & \texttt{tomcat} & 7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & 10289462 & $M$  & 2012-09-12 \\
%		\hline
%	\end{tabular} %
%}
%\end{table*}

@@

	\caption{62 QS outdated online clone pairs. Outdated clones are caused (\textit{C}) by statement modifications, added, deleted (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}

@@

	\small

@@

	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}

@@

		No. & SO Post & SO Date & Q project & Ver. & File & Start & End & Q Date & \textit{C} & $C$ Date \\

@@

			1 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjtools/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			2 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjweaver/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
			3 & 2513183 & 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			4 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
			5 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
			6 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
			7 & 11861598 & 8-Aug-12 & \texttt{eclipse-SDK} & 4.3 & \texttt{WizardDialog.java}  & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
